Adaption of the Chumbley Score to matching of bullet striation marks

### 2017-10-01 doc/paper.Rmd
bit more fleshed out

```{r data}
if (!file.exists("../data/all-sigs.rds")) {
  files <- dir("../data/signatures", pattern="csv")
  all <- data.frame()
  for (file in files) {
    tmp <- read.csv(file=file.path(path="../data/signatures", file)) 
    if (length(grep("x",names(tmp)) > 0)) tmp <- tmp %>% select(-x)
    all <- rbind(all, tmp)
  }
  saveRDS(all, file="../data/all-sigs.rds")
} else {
  all <- readRDS("../data/all-sigs.rds")
}

@@

Signatures of lands for all Hamby-44 and Hamby-252 scans made available through the NIST ballistics database \citep{nist} were considered.

@@

@@

>>>>

```{r data}
if (!file.exists("../data/all-sigs.rds")) {
  files <- dir("../data/signatures", pattern="csv")
  all <- data.frame()
  for (file in files) {
    tmp <- read.csv(file=file.path(path="../data/signatures", file)) 
    if (length(grep("x",names(tmp)) > 0)) tmp <- tmp %>% select(-x)
    all <- rbind(all, tmp)
  }
  all <- all %>% filter(land1_id < land2_id)
  saveRDS(all, file="../data/all-sigs.rds")
} else {
  all <- readRDS("../data/all-sigs.rds")
}

@@

Signatures of lands for all Hamby-44 and Hamby-252 scans made available through the NIST ballistics database \citep{nist} were considered. Both of these sets of scans are part of the larger Hamby study \citep{hamby} and each consist of twenty known bullets (two each from ten consecutively rifled Ruger P85 barrels) and fifteen questioned bullets (each matching one of the ten barrels). Ground truth for both of these Hamby sets is known and was used to assess correctness of the tests results.

We used the adjusted Chumbley method as proposed in \citet{hadler} and implemented in the R package `toolmaRk` \citep{toolmark} on all pairwise land-to-land comparisons of the Hamby scans (a total of 85,491 comparisons) in the following manner:

\hh{ XXX maybe we should include a table with an overview of the different parameter settings}

### Signatures

@@

Figure \ref{fig:type1} compares nominal (fixed) type I error and actually observed type I errors for the parameter settings in table XXX.

@@

\hh{Some of the test results are missing - we should look into the numbers and parameter settings for those.}

```{r}
ns <- all %>% group_by(wv, wo, match) %>% summarize(
  n_ss = mean(same_shift_n),
  n_ds = mean(diff_shift_n),
  miss = sum(is.na(p_value))
)
ns %>% filter(wv %in% c(30, 50)) %>% 
  ggplot(aes(x = match, y = n_ds, shape=match, colour = factor(wv))) + 
  geom_point() + geom_line(aes(group=wv)) + facet_wrap(~wo)
```
